Separating Use and Reuse to Improve Both

### 2017-05-29 FACS/Examples.tex
Section 5
.

This section sketches some of the key ideas in \name more
formally. \bruno{Could we point out here a few references of key 
ideas that were presented in other work? This would justify the 
formalization sketch better, I think.}

@@

To declare a trait \mTD\ or a class \mCD, we can use either a code literal \mL\ or a trait
expression.  Traits in full 42 come with various operators (restrict, hide,
alias) but in \name we focus on the single operator 
$\use$, taking a set
of code values: that is trait names \mt\ or literals \mL\ and composing them.  This operation, sometimes called \emph{sum}, is the simplest and most elegant
trait composition operator~\bruno{Maybe some references here would
  help}.

$\use\ \overline\mV$ composes the content of $\overline\mV$
by taking the union of the methods and the union of the
implementations.\bruno{Also, for Use, wasn't this similar to your
  previous work in FJig/DeepFJig?}
\use\ cannot be applied if multiple versions of the same method are
present in different traits.  An exception is done for abstract methods:
methods where the implementation \me\ is missing. In this case (if the
headers are compatible) the implemented version is selected.  In a sum
of two abstract methods with compatible headers, the one with the more
specific type is selected.

>>>>

This section sketches some of the key ideas in \name more
formally. 
A similarly interleaving approach can be seen in\cite{servetto2014meta} fully formalized.

@@

\noindent To declare a trait \mTD\ or a class \mCD, we can use either a code literal \mL\ or a trait
expression.  In full 42 we support with various operators (restrict, hide,
alias) but in \name we focus on the single operator 
$\use$, taking a set
of code values: that is trait names \mt\ or code literals \mL\ and composing them.  This operation, sometimes called \emph{sum}, is the simplest and most elegant
trait composition operator~\cite{ducasse2006traits}.

$\use\ \overline\mV$ composes the content of $\overline\mV$
by taking the union of the methods and the union of the
implementations.
\use\ cannot be applied if multiple versions of the same method are
present in different traits.  An exception is done for abstract methods:
methods where the implementation \me\ is missing. In this case (if the
headers are compatible) the implemented version is selected.  In a sum
of two abstract methods with compatible headers, the one with the more
specific type is selected.
